\LARGE \bf Imposing a Weight Norm Constraint for Neuro–Adaptive Control

### 2025-03-12 manuscript.tex
Move packages and macros to submodule

%In case you encounter the following error:
%Error 1010 The PDF file may be corrupt (unable to open PDF file) OR
%Error 1000 An error occurred while parsing a content stream. Unable to analyze the PDF file.
%This is a known problem with pdfLaTeX conversion filter. The file cannot be opened with acrobat reader
%Please use one of the alternatives below to circumvent this error by uncommenting one or the other
%\pdfobjcompresslevel=0
%\pdfminorversion=4

% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

% The following packages can be found on http:\\www.ctan.org
%\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed

% MY PAKEAGES ========================================
\usepackage{epsfig}
% \usepackage{lipsum}  
\usepackage{kotex}
% \usepackage{natbib}
\usepackage{cite}
\usepackage{amssymb}
\usepackage{xcolor}
% \usepackage{enumitem}
% \newlist{steps}{enumerate}{1}
% \setlist[steps, 1]{label = Step \arabic*: }

\usepackage{algorithm}
\usepackage{svg}

\usepackage{amsmath,amsfonts}
\usepackage{algorithmic}
\usepackage{array}
% \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\usepackage{subfig}
% \usepackage{textcomp}
\usepackage{stfloats}
\usepackage{url}
\usepackage{verbatim}
\usepackage{graphicx}
% \hyphenation{op-tical net-works semi-conduc-tor IEEE-Xplore}
% \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
 % T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
% \usepackage{balance}

\let\proof\relax
\let\endproof\relax
\usepackage{amsthm}

\makeatletter
\let\NAT@parse\undefined
\makeatother
\usepackage[colorlinks=true,linkcolor=black,citecolor=black]{hyperref}
% \usepackage[]{hyperref}
% \hypersetup{
%     % bookmarksnumbered=true,
%     %   linkbordercolor=blue,
%     %   filebordercolor=red,
%     %   citebordercolor = green,      
%     %   urlbordercolor=red,
%       %
%       colorlinks=false
%       % linkcolor=blue,
%       % filecolor=blue,
%       % citecolor = blue,      
%       % urlcolor=cyan,
% }

\usepackage{cleveref, autonum}

\newtheorem{remark}{Remark}
\newtheorem{assum}{Assumption}
\newtheorem{lem}{Lemma}
\newtheorem{theorem}{Theorem}

\newcommand{\etal}{\textit{et~al.\ }}
\newcommand\eg{\textit{e.g.\ }}
\newcommand\ie{\textrm{i.e.\ }}
\newcommand\R{\mathbb{R}}

\newcommand*{\mv}[1]{\boldsymbol{#1}}
\newcommand*{\mm}[1]{\boldsymbol{#1}}
\newcommand*{\norm}[1]{\lVert #1 \rVert}

\newcommand\bx{\mv x}
\newcommand\bu{\mv u}

\newcommand\der{\mathrm d}
\newcommand*{\ddfrac}[2]{
    \frac{\der {#1}}{\der {#2}}
}
\newcommand*{\ddtfrac}[2]{
    \tfrac{\der {#1}}{\der {#2}}
}

@@

\title{\LARGE \bf
Imposing a Weight Norm Constraint for Neuro–Adaptive Control
}
% Constrained Optimization-Based neuro–Adaptive Control With Weight Constraint

@@

\begin{proof}

The boundedness is proven from the last layer to the first layer.

>>>>

% \makeatletter
% \let\NAT@parse\undefined
% \makeatother

\input{dding_template/tex_packages/tex_packages_general.tex}
\input{dding_template/tex_macros/tex_macros_general.tex}

@@

\title{\LARGE \bf
Imposing a Weight Norm Constraint for Neuro–Adaptive Control
}

@@

\begin{proof}
The boundedness is proven from the last layer to the first layer.
